Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elisa Kugaevskaya for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-11 paper/paper.tex
Change the title

\title{Recovering Economic Growth Rates \\ of Unrecognized States \\ in the Former Soviet Union \\ from Nighttime Light \thanks{I thank Elisa Kugaevskaya for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.} }
\author{Masayuki Kudamatsu \thanks{Osaka School of International Public Policy, Osaka University. Email: kudamatsu@osipp.osaka-u.ac.jp}}
\date{\today}
\maketitle

>>>>

\title{Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elisa Kugaevskaya for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.} }
\author{Masayuki Kudamatsu \thanks{Osaka School of International Public Policy, Osaka University. Email: kudamatsu@osipp.osaka-u.ac.jp}}
\date{\today}
\maketitle
